HO unification from object language to meta language

### 2024-02-28 paper/main.tex
wip

\noindent
Unfortunately this translation of rule \ref{clause:r3} uses the
predicate \coqIn{P} as a first order term for the meta
language (its type is \elpiIn{tm}).
If we try to backchain the rule \ref{clause:r3} on the encoding of the goal
\ref{goal:g}:

@@

\noindent
Since \elpiIn{Pm} is an higher-order unification variable with \elpiIn{x}
in its scope, the unification problem \ref{problem:pa} admits one solution:

@@

\noindent
After unifying the head of rule \ref{clause:r3a} with the goal, Elpi runs
the premise <<\elpiIn{link Pm A P}>> that is in charge of bringing the
assignment for \elpiIn{Pm} (that has type \elpiIn{tm -> tm})
back to the domain of Coq terms:

@@

\paragraph{Contributions}
In this paper we discuss alternative encodings of Coq in
Elpi~\ref{sec:encodings}, then we identify a minimal language \Fo
in which the problems sketched here can be fully described.
We then detail an encoding \elpiIn{comp} from \Fo{} to \Ho (the language of
the meta language) and a decoding \elpiIn{decomp} to relate the unifiers
bla bla.. TODO citare Teyjus.

@@

\begin{elpicode}
app [F, con"a"] = app[F, con"a", con"a"]
\end{elpicode}

@@

\begin{elpicode}
F = lam x\app[const f,x,x]
\end{elpicode}

\noindent
becomes solvable in DTT trivially, since the term is ground (hence in \llambda),
but is one substitutes F in the LHS does not find, structurally, the RHS
hence \Ue would fail (since \Ue does not know about the $\beta$ rule of DTT).
Our compiler takes care of making property \ref{prop:simulation} hold, see
section XXX.

>>>>

\noindent
Unfortunately this translation of rule \ref{clause:r3} uses the
predicate \coqIn{P} as a first order term: for the meta
language its type is \elpiIn{tm}.
If we try to backchain the rule \ref{clause:r3} on the encoding of the goal
\ref{goal:g} given below

@@

\noindent
Since \elpiIn{Pm} is an higher-order unification variable,
of type \elpiIn{tm -> tm},
with \elpiIn{x}
in its scope, the unification problem \ref{problem:pa}
admits one solution:

@@

\noindent
After unifying the head of rule \ref{clause:r3a} with the goal, Elpi runs
the premise <<\elpiIn{link Pm A P}>> that is in charge of bringing the
assignment for \elpiIn{Pm} back to the domain \elpiIn{tm} of Coq terms:

@@

\paragraph{Contributions}
In this paper we discuss alternative encodings of Coq in
Elpi (Section~\ref{sec:encodings}), then we identify a minimal language \Fo{}
in which the problems sketched here can be fully described.
We then detail an encoding \elpiIn{comp} from \Fo{} to \Ho (the language of
the meta language) and a decoding \elpiIn{decomp} to relate the unifiers
bla bla.. TODO citare Teyjus.

@@

\begin{elpicode}
app [F, con"a"] = app[con"f", con"a", con"a"]
\end{elpicode}

@@

\begin{elpicode}
F = lam x\ app[con"f",x,x]
\end{elpicode}

\noindent
becomes solvable in DTT trivially, since the term is ground (hence in \llambda),
but if one substitutes \elpiIn{F} in the LHS does not find,
structurally, the RHS
hence \Ue would fail (since \Ue does not know about the $\beta$ rule of DTT).
Our compiler takes care of making property \ref{prop:simulation} hold, see
section XXX.
